### 2016-02-04 inputs/introduction.tex
phrasing

Imputation of missing alleles and genotypes is usually a preliminary step for

@@

data add additional complexity to the task of imputing missing genotypes: 
exploitation of linkage disequilibrium and haplotype reconstruction 

@@

or scaffolds, and overall data are less homogeneous. Rutkoski et al.~\cite{rutkoski_imputation_2013}

@@

as high as 0.84-0.94 (measured as $R^{2}$ between true and imputed genotypes). Imputation of missing GBS data without alignment to the reference genome has been reported in alfalfa (``Medicago sativa'', \cite{Rocher_validation_2015}) and red raspberry (``Rubus idaeus'', \cite{ward_saturated_2013}).\\

@@

assembled in 2005 \cite{international_rice_genome_sequencing_project_map-based_2005}, and updated in 2013 \cite{kawahara_improvement_2013},

@@

as part of Tassel suite). The four general algorithms were chosen as well known imputation strategies implemented in several freely available software libraries and frameworks. The two genotype-specific methods represent the state of the art for genotypes lacking pedigree information.\\

>>>>

Imputation of missing alleles and genotypes is a preliminary step for

@@

data add additional complexity to genotype imputation. Exploitation of linkage 
disequilibrium and haplotype reconstruction 

@@

or scaffolds, and overall data are less homogeneous.
Rutkoski et al.~\cite{rutkoski_imputation_2013}

@@

as high as 0.84-0.94 (measured as $R^{2}$ between true and imputed genotypes).
Imputation of missing GBS data without alignment to the reference genome has
been reported in alfalfa (``Medicago sativa'', \cite{Rocher_validation_2015})
and red raspberry (``Rubus idaeus'', \cite{ward_saturated_2013}). These studies
however do not focus on measuring imputation efficiency and do not compare
alternative imputation models.\\
	%un po' una ripetizione. Togliere?

@@

assembled in 2005 \cite{international_rice_genome_sequencing_project_map-based_2005},
and updated in 2013 \cite{kawahara_improvement_2013},

@@

as part of Tassel suite). The four general algorithms were chosen as well known 
imputation strategies implemented in several freely available software libraries
and frameworks. The two genotype-specific methods represent the state of the art 
for genotypes lacking pedigree information.\\
